Disparities in Climate-Induced Health Outcomes in the Greater Toronto Area.

### 2022-06-13 outputs/paper/paper.qmd
Update paper.qmd

---
title: "Disparities in Climate-Induced Health Outcomes in the Greater Toronto Area."
author: "Sarah Mansoor"
thanks: "Code and data are available at: https://github.com/sarahmansoorr/SUDS2022"
date: "`r format(Sys.time(), '%d %B %Y')`"
format: pdf
editor: visual
bstract: ""
---

@@

@@

@@

>>>>

---
title: "Disparities in Climate-Induced Health Outcomes in the Greater Toronto Area."
author: "Sarah Mansoor"
thanks: "Code and data are available at: https://github.com/sarahmansoorr/SUDS2022"
date: "`r format(Sys.time(), '%d %B %Y')`"
format: pdf
editor: visual
abstract: ""
toc: true
bibliography: references.bib
---

@@

#### Data Collection

#### Variables of Interest

#### Data Processing

#### Population, Frame or Sample

@@

#### Visual 1

#### Implications 1

#### Visual 2

#### Implications 2

#### Visuals 3

#### Implications 3

## Limitations

## Results

@@

## Conclusion
